Minimax lower bounds for source localization

### 2017-01-10 paper.tex
Add missing references.

\urlstyle{tt}

@@

This paper seeks to address the shortcomings of earlier methods by deriving
minimax lower bounds for the source localization problem, which apply to
\emph{all} estimators (biased \emph{and} unbiased), and which can give a
scaling in terms of the number of sensors used (for a fixed sensor placement
configuration). Computing the lower bound for the ``real brain model'' (where
the complete geometry of the brain surface is accounted for) is rendered very
difficult since analytical solutions for the EEG signal, given the brain
activity, do not exist. ``Spherical head
models''~\cite{Nunez2006Electric,Grover2016Information} \emph{do} have
analytical solutions, but are still not easily amenable to analytical lower
bounds because the spherical surface does not permit uniform
sampling~\cite{ImpossibilityOfSphereSampling}, and because the solution is
expressed in terms of special functions. We therefore restrict our analysis to
a source localization problem on a one-dimensional domain (to be described in
detail in Section~\ref{sec:source-localization}).

@@

\begin{IEEEproof}
Starting from equation~\eqref{eq:le-cam-bound} and working on the setting
described in Section~\ref{sec:source-localization}, we proceed to derive the
total variation distance for the distributions of interest. Using Pinsker's
inequality~\cite{Pinsker} and the convenient tensorization of the
KL-divergence~\cite{tensorization}, we see that:
\begin{equation} \label{eq:pinsker-tensorization}
	\norm{P_1^n - P_0^n}_{TV}^2 \leq \frac{1}{2} D_{KL}(P_0^n \Vert P_1^n) = \frac{n}{2} D_{KL}(P_0 \Vert P_1)
\end{equation}
For multivariate normal distributions with the same covariance, the
KL-divergence is given by
\begin{equation} \label{eq:kl-div-normal}
	D_{KL}(P_0 \Vert P_1) = (\v \mu_0 - \v \mu_1)^T \m \Sigma^{-1} (\v \mu_0 - \v \mu_1)
\end{equation}
where $\v \mu_0$ and $\v \mu_1$ are the means of $P_0$ and $P_1$
respectively~\cite{KLDivNormal}.

@@

Another simple extension takes our problem from a one-dimensional setting to a
$d$-dimensional setting. Here, we would have $\v\theta \in [0, T)^d$, and the
$\ell_2$ loss function, $\Phiorho(\v\theta, \vhat\theta) = \norm{\v\theta -
\vhat\theta}^2$. Then, using Assouad's lemma~\cite{Tsybakov} in the manner
described in~\cite{Duchi2015Information}, we can split the minimax risk
along each of the $d$ dimensions, and bound each separately using Le Cam's
method.

>>>>

@@

This paper seeks to address the shortcomings of earlier methods by deriving
minimax lower bounds for the source localization problem, which apply to
\emph{all} estimators (biased \emph{and} unbiased), and which can give a
scaling in terms of the number of sensors used (for a fixed sensor placement
configuration). Computing the lower bound for the ``real brain model'' (where
the complete geometry of the brain surface is accounted for) is rendered very
difficult since analytical solutions for the EEG signal, given the brain
activity, do not exist. ``Spherical head
models''~\cite{Nunez2006Electric,Grover2016Information} \emph{do} have
analytical solutions, but are still not easily amenable to analytical lower
bounds because the spherical surface does not permit uniform
sampling~\cite{Heath1956Thirteen}, and because the solution is expressed in
terms of special functions. We therefore restrict our analysis to a source
localization problem on a one-dimensional domain (to be described in detail in
Section~\ref{sec:source-localization}).

@@

\begin{IEEEproof}
Starting from equation~\eqref{eq:le-cam-bound} and working on the setting
described in Section~\ref{sec:source-localization}, we proceed to derive the
total variation distance for the distributions of interest. Using Pinsker's
inequality~\cite{Kullback1967Lower} and the convenient tensorization of the
KL-divergence~\cite{Duchi2015Information}, we see that:
\begin{equation} \label{eq:pinsker-tensorization}
	\norm{P_1^n - P_0^n}_{TV}^2 \leq \frac{1}{2} D_{KL}(P_0^n \Vert P_1^n) = \frac{n}{2} D_{KL}(P_0 \Vert P_1)
\end{equation}
For multivariate normal distributions with the same covariance, the
KL-divergence is given by
\begin{equation} \label{eq:kl-div-normal}
	D_{KL}(P_0 \Vert P_1) = (\v \mu_0 - \v \mu_1)^T \m \Sigma^{-1} (\v \mu_0 - \v \mu_1)
\end{equation}
where $\v \mu_0$ and $\v \mu_1$ are the means of $P_0$ and $P_1$
respectively~\cite{DuchiDerivation}.

@@

Another simple extension takes our problem from a one-dimensional setting to a
$d$-dimensional setting. Here, we would have $\v\theta \in [0, T)^d$, and the
$\ell_2$ loss function, $\Phiorho(\v\theta, \vhat\theta) = \norm{\v\theta -
\vhat\theta}^2$. Then, using Assouad's lemma~\cite{Tsybakov2009Introduction} in
the manner described in~\cite{Duchi2015Information}, we can split the minimax
risk along each of the $d$ dimensions, and bound each separately using Le Cam's
method.
